---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

I am going to need tidyverse so just loading that up here.

```{r, warning=FALSE, results='hide'}
library(tidyverse)
```

## Loading and preprocessing the data

The problem states

>The variables included in this dataset are:<br>
>steps: Number of steps taking in a 5-minute interval (missing values are coded as NA)<br>
>date: The date on which the measurement was taken in YYYY-MM-DD format<br>
>interval: Identifier for the 5-minute interval in which measurement was taken<br>
>The dataset is stored in a comma-separated-value (CSV) file and there are a total of 17,568 >observations in this dataset.

```{r}
activity = read_csv('activity/activity.csv', col_types = cols(
  steps = col_double(),
  date = col_date(),
  interval = col_integer()
))
head(activity)
summary(activity)
```

Looks sort of right. The steps are 0 a lot. Perhaps people are sleeping?

## What is mean total number of steps taken per day?

```{r}
all_daily_mean_steps = summarize(group_by(activity, date), mean_steps=mean(steps))
all_daily_mean_steps
```

Those NAs are making me nervous, so let's drop them:
```{r}
activity_lite = drop_na(activity)
daily_mean_steps = summarize(group_by(activity_lite, date), daily_mean_steps=mean(steps))
daily_mean_steps
```

That looks better, so now I can just look at the average

```{r}
mean(daily_mean_steps$daily_mean_steps)
```


## What is the average daily activity pattern?

We already have this so let's just look at it.

```{r}
plot(daily_mean_steps, type="l")
```

No, the question asked for steps over the time of day over all days.

```{r}
interval_mean_steps = summarize(group_by(activity_lite, interval), interval_mean_steps=mean(steps))
interval_mean_steps
plot(interval_mean_steps, type="l")
```

Yikes, expected that to be a lot smoother.
However, the quiet time while the user sleeps and then that commute/run in the morning makes sense.

## Imputing missing values

We could replace the steps by the average for the day or the interval.
I can imagine that the interval is more important (you sleep at midnight whether or not you took a hike earlier)
Or we can just use the local information before and after to do a fill.
The problem with the local information is that it can change pretty sharply, so if most of the NAs are at night, and it stopped collecting during a walk, we don't want it to show the person walking all night.


```{r}
a = left_join(activity, interval_mean_steps, by = "interval")
a$steps[is.na(a$steps)] <- a$interval_mean_steps[is.na(a$steps)]
```

The original steps had a mean and median of:

```{r}
mean(activity_lite$steps)
median(activity_lite$steps)
```
And the modified one has a mean and median of:
```{r}
mean(a$steps)
median(a$steps)
```



```{r}
hist(a$steps)
hist(activity$steps)
```

## Are there differences in activity patterns between weekdays and weekends?
